A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-06-07 main.tex
Write the paragraph of 多段階計算とは何か?

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bcprules, proof}
\usepackage{fancybox}
\usepackage{mathtools}
\usepackage{float}
\usepackage{xparse}
% \usepackage{ebproof}
\usepackage{lscape}
\usepackage{mdframed}
\usepackage{xspace}

@@

Multistage programming enable us to generate and run fragments of code at runtime.

@@

A type judgement of \LTP is of the form $\G \vdash M : \tau @ A$.
Transition $A$ means in which transition $M$ exists.
Therefore, transitions appear in typing rules, too.
\begin{center}
    \infrule{\G\vdash M:\tau@{A\alpha}}{\G\vdash \TB_{\alpha}M:\TW_{\alpha}\tau@A}{\TTB} \andalso
    \infrule{\G\vdash M:\TW_{\alpha}\tau@A}{\G\vdash \TBL_{\alpha}M:\tau@{A\alpha}}{\TTBL}
\end{center}
\TTB, corresponding to quoting, means 
if $M$ is typed $\tau$ at transition $A\alpha$ then $\TB_{\alpha}M$, quoted $M$, is typed $\TW_{\alpha}\tau$ at $A$.
\TTBL is converse of \TTB.

@@

% \LLF
\LLF is a simple system of dependent types introduced in \cite{attapl}.
\red{system / type system / calculus ?}
It is based on Edinburgh LF\cite{harper1993framework}.
Therefore, all constants and base types are declared in the signature.
The \LLF type theory generalizes simply typed lambda calculus
by replacing the function type $\tau\to\sigma$ with the dependent product type $\Pi x:\tau.\sigma$.

@@

Second, we need kinding rules and well-formed kinding rules in order to extend \LMD with dependent types.
It was lucky that almost all rules are determined easily.
This is because multistage calculus and dependent types are almost orthogonal.
\red{orthogonal は抽象的すぎるか?}
Therefore, we can get kinding rules and well-formed kinding rules of \LMD just by 
attaching stage anotations to ones of \LLF.
For example, \KAbs-LF is a kinding rule for a dependent type in \LLF and \KAbs\ is a corresponding one.
\begin{center}
    \infrule{\G\vdash \tau :: * \andalso \G,x:\tau@A\vdash \sigma::J}{\G\vdash(\Pi x:\tau.\sigma) :: (\Pi x:\tau.J)}{\KAbs-LF} \\[2mm]
    \infrule{\G\V \tau :: *@A \andalso \G,x:\tau@A\V \sigma::J@A}{\G\V(\Pi x:\tau.\sigma) :: (\Pi x:\tau.J)@A}{\KAbs} \\[2mm]
\end{center}

@@

The biggest problem in extension is handling the CSP symbol $\%_\alpha$ in \LMD.
The equivalence simple rule to handle CSP is \QCsp.
\begin{center}
    \infrule{\G\V M \E N : \tau @A}{\G\V\%_\alpha M \E \%_\alpha N : \tau@{A\alpha}}{\QCsp}
\end{center}
However, this rule isn't enough when the parameters of dependent types are cross-staed.
We will discuss this problem in a later section and solve this problem with the new rule \QPercent.
\begin{center}
    \infrule{\G\V M:\tau@{A\alpha} \andalso \G\V M:\tau@A}{\G\V\%_\alpha M \E M : \tau@{A\alpha}}{\QPercent}
\end{center}
\red{この段落でQ-Cspの持つ問題点を指摘すべきか? ただ、ここでmulmatの例を使うと3章と被る。}

@@

\begin{align*}
	\textrm{Type variables}  &  &                          & X,Y,Z                                                                             \\
	\textrm{Constants}       &  &                          & c                                                                                 \\
	\textrm{Variables}       &  &                          & x,y,z                                                                             \\
	\textrm{Stage variables} &  &                          & \alpha,\beta,\gamma                                                               \\
	\textrm{Stage}           &  &                          & A,B,C                                                                             \\
	\textrm{Kinds}           &  & K,J,I,H,G                & ::= * \mid \Pi x:\tau.K                                                           \\
	\textrm{Types}           &  & \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\tau \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \\
	\textrm{Terms}           &  & M,N,L,O,P                & ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M 
	\mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ \epsilon \mid \%_\alpha M                                                                  \\ 
	\textrm{Signature}       &  & \Sigma                   & ::= \phi \mid X::K \mid c:\tau                                                    \\
	\textrm{Contexts}        &  & \Gamma                   & ::= \phi \mid  \Gamma,x:\tau@A\ (x\not\in\textrm{FV}(\G))                         \\
\end{align*}

@@

\begin{figure}
	\begin{center}
		\infrule{c:\tau \in \Sigma \andalso \G\V \tau::*@A}{\G \V c:\tau@A}{\TConst} \andalso
		\infrule{x:\tau@A \in \G \andalso \G\V \tau::*@A}{\G \V x:\tau@A}{\TVar} \\[2mm]
		\infrule{\G\V \sigma::*@A\andalso\G,x:\sigma@A\V M:\tau@A}{\G\V(\lambda (x:\sigma).M):(\Pi (x:\sigma).\tau)@A}{\textsc{T-Abs}} \\[2mm]
		\infrule{\G\V M:(\Pi (x:\sigma).\tau)@A \andalso \G\V N:\sigma@A}{\G\V M\ N : \tau[x\mapsto N]@A}{\textsc{T-App}} \andalso
		\infrule{\G\V M:\tau@A \andalso \G\V \tau\equiv \sigma :: K@A}{\G\V M:\sigma@A}{\textsc{T-Conv}} \\[2mm]
		\infrule{\G\V M:\tau@{A\alpha}}{\G\V\TB_{\alpha}M:\TW_{\alpha}\tau@A}{\TTB} \andalso
		\infrule{\G\V M:\TW_{\alpha}\tau@A}{\G\V\TBL_{\alpha}M:\tau@{A\alpha}}{\TTBL} \\[2mm]
		\infrule{\G\V M:\tau@A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V\Lambda\alpha.M:\forall\alpha.\tau@A}{\textsc{T-Gen}} \andalso
		\infrule{\G\V M:\forall\alpha.\tau@A}{\G\V M\ \epsilon:\tau[\alpha \mapsto \epsilon]@A}{\textsc{T-Ins}} \andalso
		\infrule{\G\V M:\tau@A}{\G\V \%_\alpha M:\tau@{A\alpha}}{\textsc{T-Csp}} \andalso
		\caption{Typing Rules}
		\label{fig:typing-rules}
	\end{center}
\end{figure}

@@

\begin{figure}
	\begin{center}
		\infrule{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau@A \V \rho \E \pi :: *@A}{\G\V\Pi x:\tau.\rho \E \Pi x:\sigma.\pi :: *@A}{\QTAbs} \\[2mm]
		\infrule{\G\V \tau \E \sigma :: (\Pi x:\rho.K)@A \andalso \G\V M \E N : \rho @A}{\G\V \tau\ M \E \sigma\ N :: K[x \mapsto M]@A}{\QTApp} \\[2mm]
		\infrule{\G\V \tau \E \sigma :: *@{A\alpha}}{\G\V \TW_{\alpha} \tau \E \TW_{\alpha} \sigma :: *@A}{\textsc{QT-$\TW$}}\andalso
		\infrule{\G\V \tau \E \sigma :: K@A}{\G\V \tau \E \sigma :: K@{A\alpha}}{\textsc{QT-Csp}} \\[2mm]
		\infrule{\G\V \tau \E \sigma :: *@A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V \forall\alpha.\tau \E  \forall\alpha.\sigma :: *@A}{\textsc{QT-Gen}} \\[2mm]
		\infrule{\G\V \tau::K@A}{\G\V \tau\E\tau :: K@A}{\textsc{QT-Refl}} \andalso
		\infrule{\G\V \tau \E \sigma :: K@A}{\G\V \sigma \E \tau :: K@A}{\textsc{QT-Sym}} \\[2mm]
		\infrule{\G\V \tau \E \sigma :: K@A \andalso \G\V \sigma \E \rho  :: K@A}{\G\V \tau \E \rho  :: K@A}{\textsc{QT-Trans}}
		\caption{Type Equivalence Rules}
		\label{fig:type-equivalence-rules}
	\end{center}
\end{figure}

@@

\begin{figure}
	\begin{center}
		\infrule{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau@A \V M \E N : \rho @A}{\G\V\lambda x:\tau.M \E \lambda x:\sigma.N : (\Pi x:\tau.\rho)@A}{\QAbs} \\[2mm]
		\infrule{\G\V M \E L : (\Pi x:\sigma.\tau)@A \andalso \G\V N \E O : \sigma@A}{\G\V M\ N \E L\ O : \tau[x \mapsto N]@A}{\QApp} \\[2mm]
		\infrule{\G\V M \E N : \tau@{A\alpha}}{\G\V \TB_\alpha M \E \TB_\alpha N : \TW_\alpha \tau@A}{\QTB} \andalso
		\infrule{\G\V M \E N : \TW_\alpha \tau@A}{\G\V \TBL_\alpha M \E \TBL_\alpha N : \tau@{A\alpha}}{\QTBL} \\[2mm]
		\infrule{\G\V M\E N : \tau@A \andalso \alpha \notin \FTV(\G)\cup\FTV(A)}{\G\V \Lambda\alpha.M \E \Lambda\alpha.N : \forall\alpha.\tau@A}{\QGen} \\[2mm]
		\infrule{\G\V M \E N:\forall\alpha.\tau@A}{\G\V M\ \epsilon \E N\ \epsilon : \tau[\alpha \mapsto \epsilon]@A}{\QIns}\andalso
		\infrule{\G\V M \E N : \tau @A}{\G\V\%_\alpha M \E \%_\alpha N : \tau@{A\alpha}}{\QCsp} \\[2mm]
		\infrule{\G\V M:\tau@A}{\G\V M\E M : \tau@A}{\QRefl} \andalso
		\infrule{\G\V M\E N : \tau@A}{\G\V N\E M : \tau@A}{\QSym} \\[2mm]
		\infrule{\G\V M\E N : \tau@A \andalso \G\V N\E L : \tau@A}{\G\V M\E L : \tau@A}{\QTrans} \\[2mm]
		\infrule{\G,x:\sigma@A\V M:\tau@A \andalso \G\V N:\sigma@A}{\G\V(\lambda x:\sigma.M)\ N\E M[x\mapsto N] : \tau[x \mapsto N]@A}{\QBeta} \\[2mm]
		% \infrule{\G\V M:(\Pi x:\sigma.\tau)@A \andalso x\notin \text{FV}(M)}{\G\V(\lambda x:\sigma.M\ x)\E M: (\Pi x:\sigma.\tau)@A}{\QEta} \\[2mm]
		\infrule{\G\V M \E N : \tau@A}{\G\V \TBL_\alpha(\TB_\alpha M) \E N : \tau @A}{\QTBLTB} \\[2mm]
		\infrule{\G\V (\Lambda\alpha.M) : \forall\alpha.\tau@A}{\G\V (\Lambda\alpha.M)\ \epsilon \E M[\alpha \mapsto \epsilon] : \tau[\alpha \mapsto \epsilon]@A}{\QLambda} \\[2mm]
		\infrule{\G\V M:\tau@{A\alpha} \andalso \G\V M:\tau@A}{\G\V\%_\alpha M \E M : \tau@{A\alpha}}{\QPercent}
		\caption{Term Equivalence Rules}
		\label{fig:term-equivalence-rules}
	\end{center}
\end{figure}

@@

Following three inversion lemmas are needed in proving later theorems.
\begin{lemma}[Inversion Lemma for $\Pi$ type]
	If $\G \V (\lambda x:\sigma.M) : (\Pi x:\sigma'.\tau)@A$ then
	\begin{enumerate}
		\item $\G \V \sigma \E \sigma'@A$
		\item $\G ,x:\sigma@A\V M:\tau@A$
	\end{enumerate}
	\item If $\G \V \rho \E (\Pi x:\sigma.\tau) : K @A$ then $\exists \sigma', \tau', K, J$ such that
	\begin{enumerate}
		\item $\rho = \Pi x:\sigma'.\tau'$
		\item $\G \V \sigma \E \sigma' : K @A$
		\item $\G, x:\sigma@A\V \tau \E \tau' : J @A$
	\end{enumerate}
	\item If $\G \V (\Pi x:\sigma.\tau) \E \rho : K @A$ then $\exists \sigma', \tau', K, J$ such that
	\begin{enumerate}
		\item $\rho = \Pi x:\sigma'.\tau'$
		\item $\G \V \sigma \E \sigma' : K @A$
		\item $\G, x:\sigma@A\V \tau \E \tau' : J @A$
	\end{enumerate}
\end{lemma}

@@

\begin{theorem}[Inversion Lemma for $\TW$ type]
	\begin{item}
	      \item If $\G \V \TB_\alpha M : \TW_\alpha \tau@A$ then $\G \V M : \tau @A$.
	      \item If $\G \V \rho \E  \TW_\alpha \tau : K @A$ then $\exists \tau', K, J$ such that
	      \begin{enumerate}
		      \item $\rho = \TW_\alpha \tau'$
		      \item $\G @A\V \tau \E \tau' : K @A$
	      \end{enumerate}
	      \item If $\G \V \TW_\alpha \tau \E \rho : K @A$ then $\exists \tau', K, J$ such that
	      \begin{enumerate}
		      \item $\rho = \TW_\alpha \tau'$
		      \item $\G @A\V \tau \E \tau' : K @A$
	      \end{enumerate}
	\end{item}
\end{theorem}

@@

\begin{theorem}[Inversion Lemma for $\Lambda$ type]
	\begin{item}
	      \item If $\G \V \Lambda\alpha.M : \forall\alpha.\tau@A$ then $\G \V M : \tau @A$ and $\alpha \notin \FTV(\G) \cup \FV(A)$.
	      \item If $\G \V \rho \E \forall\alpha.\tau : K @A$ then $\exists \tau', K$ such that
	      \begin{enumerate}
		      \item $\rho = \forall\alpha.\tau'$
		      \item $\G \V \tau \E \tau' : K @A$
	      \end{enumerate}
	      \item If $\G \V \forall\alpha.\tau \E \rho : K @A$ then $\exists \tau', K$ such that
	      \begin{enumerate}
		      \item $\rho = \forall\alpha.\tau'$
		      \item $\G \V \tau \E \tau' : K @A$
	      \end{enumerate}
	\end{item}
\end{theorem}

@@

\begin{theorem}[Unique Decomposition]
	If $x:\tau@\epsilon \notin \G$ and $\G \V M : \tau @ A$ then 1 or 2 is true.
	\begin{enumerate}
		\item $ M \in V^A$
		\item There exist an unique tuple of $B, E^A_B, R^B$ such that $M = E^A_B[R^B]$ ($B = \epsilon$ or $B = \beta$) .
	\end{enumerate}
\end{theorem}

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bcprules, proof}
\usepackage{fancybox}
\usepackage{mathtools}
\usepackage{float}
\usepackage{xparse}
\usepackage{lscape}
\usepackage{mdframed}
\usepackage{xspace}

@@

Multistage programming enable us to generate and run fragments of code at runtime.
MetaOCaml\cite{oleg2014} provide features for multistage programming, which are quote, unquote, and running code.
Quote, written \verb|.< e >.| in MetaOCaml, makes a code value from \verb|e|.
Run, written \verb| run e | in MetaOCaml, runs a code value of \verb|e| and restore \verb|e|.
Unqote, written \verb| .~ e | in MetaOCaml, expands a code value of \verb|e|.
Unlike run, unquote is supposed to use in quote, that is, unquote cannot be used as alternative of run.
For example, the following MetaOCaml expression

\begin{verbatim}
        let a = .< fun x -> x + 1 >. in .< .~a 2 >.
\end{verbatim}

evaluates to \verb|.< (fun x -> x + 1) 2 >.|. We can get the result with run.

\begin{verbatim}
        run (let a = .< fun x -> x + 1 >. in .< .~a 2 >.)
\end{verbatim}

is reduced to 3.

@@

A type judgement of \LTP is of the form $\G \vdash M : \tau @ A$.
Transition $A$ means in which transition $M$ exists.
Therefore, transitions appear in typing rules, too.
\begin{center}
    \infrule{\G\vdash M:\tau @{A\alpha}}{\G\vdash \TB_{\alpha}M:\TW_{\alpha}\tau @A}{\TTB} \andalso
    \infrule{\G\vdash M:\TW_{\alpha}\tau @A}{\G\vdash \TBL_{\alpha}M:\tau @{A\alpha}}{\TTBL}
\end{center}
\TTB, corresponding to quoting, means 
if $M$ is typed $\tau$ at transition $A\alpha$ then $\TB_{\alpha}M$, quoted $M$, is typed $\TW_{\alpha}\tau$ at $A$.
\TTBL is converse of \TTB.

@@

% \LLF
\LLF is a simple system of dependent types introduced in \cite{attapl}.
\red{system / type system / calculus?}
It is based on Edinburgh LF\cite{harper1993framework}.
Therefore, all constants and base types are declared in the signature.
The \LLF type theory generalizes simply typed lambda calculus
by replacing the function type $\tau\to\sigma$ with the dependent product type $\Pi x:\tau.\sigma$.

@@

Second, we need kinding rules and well-formed kinding rules in order to extend \LMD with dependent types.
It was lucky that almost all rules are determined easily.
This is because multistage calculus and dependent types are almost orthogonal.
\red{orthogonal は抽象的すぎるか?}
Therefore, we can get kinding rules and well-formed kinding rules of \LMD just by 
attaching stage anotations to ones of \LLF.
For example, \KAbs-LF is a kinding rule for a dependent type in \LLF and \KAbs\ is a corresponding one.
\begin{center}
    \infrule{\G\vdash \tau :: * \andalso \G,x:\tau @A\vdash \sigma::J}{\G\vdash(\Pi x:\tau.\sigma) :: (\Pi x:\tau.J)}{\KAbs-LF} \\[2mm]
    \infrule{\G\V \tau :: *@A \andalso \G,x:\tau @A\V \sigma::J@A}{\G\V(\Pi x:\tau.\sigma) :: (\Pi x:\tau.J)@A}{\KAbs} \\[2mm]
\end{center}

@@

The biggest problem in extension is handling the CSP symbol $\%_\alpha$ in \LMD.
The equivalence simple rule to handle CSP is \QCsp.
\begin{center}
    \infrule{\G\V M \E N : \tau @A}{\G\V\%_\alpha M \E \%_\alpha N : \tau @{A\alpha}}{\QCsp}
\end{center}
However, this rule isn't enough when the parameters of dependent types are cross-staed.
We will discuss this problem in a later section and solve this problem with the new rule \QPercent.
\begin{center}
    \infrule{\G\V M:\tau @{A\alpha} \andalso \G\V M:\tau @A}{\G\V\%_\alpha M \E M : \tau @{A\alpha}}{\QPercent}
\end{center}
\red{この段落でQ-Cspの持つ問題点を指摘すべきか? ただ、ここでmulmatの例を使うと3章と被る。}

@@

\begin{align*}
	\textrm{Type variables}  &  &                          & X,Y,Z                                                                             \\
	\textrm{Constants}       &  &                          & c                                                                                 \\
	\textrm{Variables}       &  &                          & x,y,z                                                                             \\
	\textrm{Stage variables} &  &                          & \alpha,\beta,\gamma                                                               \\
	\textrm{Stage}           &  &                          & A,B,C                                                                             \\
	\textrm{Kinds}           &  & K,J,I,H,G                & ::= * \mid \Pi x:\tau.K                                                           \\
	\textrm{Types}           &  & \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\tau \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau \\
	\textrm{Terms}           &  & M,N,L,O,P                & ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M 
	\mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ \epsilon \mid \%_\alpha M                                                                  \\ 
	\textrm{Signature}       &  & \Sigma                   & ::= \phi \mid X::K \mid c:\tau                                                    \\
	\textrm{Contexts}        &  & \Gamma                   & ::= \phi \mid  \Gamma,x:\tau @A\ (x\not\in\textrm{FV}(\G))                         \\
\end{align*}

@@

\begin{figure}
	\begin{center}
		\infrule{c:\tau \in \Sigma \andalso \G\V \tau::*@A}{\G \V c:\tau @A}{\TConst} \andalso
		\infrule{x:\tau @A \in \G \andalso \G\V \tau::*@A}{\G \V x:\tau @A}{\TVar} \\[2mm]
		\infrule{\G\V \sigma::*@A\andalso\G,x:\sigma@A\V M:\tau @A}{\G\V(\lambda (x:\sigma).M):(\Pi (x:\sigma).\tau)@A}{\textsc{T-Abs}} \\[2mm]
		\infrule{\G\V M:(\Pi (x:\sigma).\tau)@A \andalso \G\V N:\sigma@A}{\G\V M\ N : \tau[x\mapsto N]@A}{\textsc{T-App}} \andalso
		\infrule{\G\V M:\tau @A \andalso \G\V \tau\equiv \sigma :: K@A}{\G\V M:\sigma@A}{\textsc{T-Conv}} \\[2mm]
		\infrule{\G\V M:\tau @{A\alpha}}{\G\V\TB_{\alpha}M:\TW_{\alpha}\tau @A}{\TTB} \andalso
		\infrule{\G\V M:\TW_{\alpha}\tau @A}{\G\V\TBL_{\alpha}M:\tau @{A\alpha}}{\TTBL} \\[2mm]
		\infrule{\G\V M:\tau @A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V\Lambda\alpha.M:\forall\alpha.\tau @A}{\textsc{T-Gen}} \andalso
		\infrule{\G\V M:\forall\alpha.\tau @A}{\G\V M\ \epsilon:\tau[\alpha \mapsto \epsilon]@A}{\textsc{T-Ins}} \andalso
		\infrule{\G\V M:\tau @A}{\G\V \%_\alpha M:\tau @{A\alpha}}{\textsc{T-Csp}} \andalso
		\caption{Typing Rules}
		\label{fig:typing-rules}
	\end{center}
\end{figure}

@@

\begin{figure}
	\begin{center}
		\infrule{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau @A \V \rho \E \pi :: *@A}{\G\V\Pi x:\tau.\rho \E \Pi x:\sigma.\pi :: *@A}{\QTAbs} \\[2mm]
		\infrule{\G\V \tau \E \sigma :: (\Pi x:\rho.K)@A \andalso \G\V M \E N : \rho @A}{\G\V \tau\ M \E \sigma\ N :: K[x \mapsto M]@A}{\QTApp} \\[2mm]
		\infrule{\G\V \tau \E \sigma :: *@{A\alpha}}{\G\V \TW_{\alpha} \tau \E \TW_{\alpha} \sigma :: *@A}{\textsc{QT-$\TW$}}\andalso
		\infrule{\G\V \tau \E \sigma :: K@A}{\G\V \tau \E \sigma :: K@{A\alpha}}{\textsc{QT-Csp}} \\[2mm]
		\infrule{\G\V \tau \E \sigma :: *@A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V \forall\alpha.\tau \E  \forall\alpha.\sigma :: *@A}{\textsc{QT-Gen}} \\[2mm]
		\infrule{\G\V \tau::K@A}{\G\V \tau\E\tau :: K@A}{\textsc{QT-Refl}} \andalso
		\infrule{\G\V \tau \E \sigma :: K@A}{\G\V \sigma \E \tau :: K@A}{\textsc{QT-Sym}} \\[2mm]
		\infrule{\G\V \tau \E \sigma :: K@A \andalso \G\V \sigma \E \rho  :: K@A}{\G\V \tau \E \rho  :: K@A}{\textsc{QT-Trans}}
		\caption{Type Equivalence Rules}
		\label{fig:type-equivalence-rules}
	\end{center}
\end{figure}

@@

\begin{figure}
	\begin{center}
		\infrule{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau @A \V M \E N : \rho @A}{\G\V\lambda x:\tau.M \E \lambda x:\sigma.N : (\Pi x:\tau.\rho)@A}{\QAbs} \\[2mm]
		\infrule{\G\V M \E L : (\Pi x:\sigma.\tau)@A \andalso \G\V N \E O : \sigma@A}{\G\V M\ N \E L\ O : \tau[x \mapsto N]@A}{\QApp} \\[2mm]
		\infrule{\G\V M \E N : \tau @{A\alpha}}{\G\V \TB_\alpha M \E \TB_\alpha N : \TW_\alpha \tau @A}{\QTB} \andalso
		\infrule{\G\V M \E N : \TW_\alpha \tau @A}{\G\V \TBL_\alpha M \E \TBL_\alpha N : \tau @{A\alpha}}{\QTBL} \\[2mm]
		\infrule{\G\V M\E N : \tau @A \andalso \alpha \notin \FTV(\G)\cup\FTV(A)}{\G\V \Lambda\alpha.M \E \Lambda\alpha.N : \forall\alpha.\tau @A}{\QGen} \\[2mm]
		\infrule{\G\V M \E N:\forall\alpha.\tau @A}{\G\V M\ \epsilon \E N\ \epsilon : \tau[\alpha \mapsto \epsilon]@A}{\QIns}\andalso
		\infrule{\G\V M \E N : \tau @A}{\G\V\%_\alpha M \E \%_\alpha N : \tau @{A\alpha}}{\QCsp} \\[2mm]
		\infrule{\G\V M:\tau @A}{\G\V M\E M : \tau @A}{\QRefl} \andalso
		\infrule{\G\V M\E N : \tau @A}{\G\V N\E M : \tau @A}{\QSym} \\[2mm]
		\infrule{\G\V M\E N : \tau @A \andalso \G\V N\E L : \tau @A}{\G\V M\E L : \tau @A}{\QTrans} \\[2mm]
		\infrule{\G,x:\sigma@A\V M:\tau @A \andalso \G\V N:\sigma@A}{\G\V(\lambda x:\sigma.M)\ N\E M[x\mapsto N] : \tau[x \mapsto N]@A}{\QBeta} \\[2mm]
		% \infrule{\G\V M:(\Pi x:\sigma.\tau)@A \andalso x\notin \text{FV}(M)}{\G\V(\lambda x:\sigma.M\ x)\E M: (\Pi x:\sigma.\tau)@A}{\QEta} \\[2mm]
		\infrule{\G\V M \E N : \tau @A}{\G\V \TBL_\alpha(\TB_\alpha M) \E N : \tau @A}{\QTBLTB} \\[2mm]
		\infrule{\G\V (\Lambda\alpha.M) : \forall\alpha.\tau @A}{\G\V (\Lambda\alpha.M)\ \epsilon \E M[\alpha \mapsto \epsilon] : \tau[\alpha \mapsto \epsilon]@A}{\QLambda} \\[2mm]
		\infrule{\G\V M:\tau @{A\alpha} \andalso \G\V M:\tau @A}{\G\V\%_\alpha M \E M : \tau @{A\alpha}}{\QPercent}
		\caption{Term Equivalence Rules}
		\label{fig:term-equivalence-rules}
	\end{center}
\end{figure}

@@

Following three inversion lemmas are needed in proving later theorems.
\begin{lemma}[Inversion Lemma for $\Pi$ type]
	If $\G \V (\lambda x:\sigma.M) : (\Pi x:\sigma'.\tau)@A$ then
	\begin{enumerate}
		\item $\G \V \sigma \E \sigma'@A$
		\item $\G ,x:\sigma@A\V M:\tau @A$
	\end{enumerate}
	\item If $\G \V \rho \E (\Pi x:\sigma.\tau) : K @A$ then $\exists \sigma', \tau', K, J$ such that
	\begin{enumerate}
		\item $\rho = \Pi x:\sigma'.\tau'$
		\item $\G \V \sigma \E \sigma' : K @A$
		\item $\G, x:\sigma@A\V \tau \E \tau' : J @A$
	\end{enumerate}
	\item If $\G \V (\Pi x:\sigma.\tau) \E \rho : K @A$ then $\exists \sigma', \tau', K, J$ such that
	\begin{enumerate}
		\item $\rho = \Pi x:\sigma'.\tau'$
		\item $\G \V \sigma \E \sigma' : K @A$
		\item $\G, x:\sigma@A\V \tau \E \tau' : J @A$
	\end{enumerate}
\end{lemma}

@@

\begin{theorem}[Inversion Lemma for $\TW$ type]
	\begin{item}
	      \item If $\G \V \TB_\alpha M : \TW_\alpha \tau @A$ then $\G \V M : \tau @A$.
	      \item If $\G \V \rho \E  \TW_\alpha \tau : K @A$ then $\exists \tau', K, J$ such that
	      \begin{enumerate}
		      \item $\rho = \TW_\alpha \tau'$
		      \item $\G @A\V \tau \E \tau' : K @A$
	      \end{enumerate}
	      \item If $\G \V \TW_\alpha \tau \E \rho : K @A$ then $\exists \tau', K, J$ such that
	      \begin{enumerate}
		      \item $\rho = \TW_\alpha \tau'$
		      \item $\G @A\V \tau \E \tau' : K @A$
	      \end{enumerate}
	\end{item}
\end{theorem}

@@

\begin{theorem}[Inversion Lemma for $\Lambda$ type]
	\begin{item}
	      \item If $\G \V \Lambda\alpha.M : \forall\alpha.\tau @A$ then $\G \V M : \tau @A$ and $\alpha \notin \FTV(\G) \cup \FV(A)$.
	      \item If $\G \V \rho \E \forall\alpha.\tau : K @A$ then $\exists \tau', K$ such that
	      \begin{enumerate}
		      \item $\rho = \forall\alpha.\tau'$
		      \item $\G \V \tau \E \tau' : K @A$
	      \end{enumerate}
	      \item If $\G \V \forall\alpha.\tau \E \rho : K @A$ then $\exists \tau', K$ such that
	      \begin{enumerate}
		      \item $\rho = \forall\alpha.\tau'$
		      \item $\G \V \tau \E \tau' : K @A$
	      \end{enumerate}
	\end{item}
\end{theorem}

@@

\begin{theorem}[Unique Decomposition]
	If $x:\tau @\epsilon \notin \G$ and $\G \V M : \tau @ A$ then 1 or 2 is true.
	\begin{enumerate}
		\item $ M \in V^A$
		\item There exist an unique tuple of $B, E^A_B, R^B$ such that $M = E^A_B[R^B]$ ($B = \epsilon$ or $B = \beta$) .
	\end{enumerate}
\end{theorem}
